---
title: "aer13_OriginalHomeworkCode_02"
author: "Abby_Robinson"
date: "9/22/2021"
output: html_document
---
#Homework 2: Titis in the Mist…
##Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

1. What is the probability that she will hear more than 8 calls during any given session?

```{r}
?dpois()
x <- c(8:30) #I wasn't sure how to code for more than 8 calls, so I set 30 as the maximum and used the c() function to show that x includes all values between 8 and 30... I don't think that is right but here we are... 
l <- 15 #set the mean equal to "l"
one <- dpois(x = x, lambda = l, log = FALSE) #X is the appropriate Poisson random variable and lambda is the mean 
probability <- sum(one) #use the sum() function to "sum" the probabilities that she will hear each number of calls between 8 and 30 to get the probability that she will hear more than 8 calls 
probability
```

NK: dpois gives you the probability that you will hear exactly a certain number of calls. ppois gives you the probability that you will hear 8 or fewer calls given a probability distribution based on the average of 15 calls per session. To use this function you would put ppois(x, lambda) where you want to know the proability that you will hear x or more calls in a session when lambda is the expected average. In this case, x is 8 and lambda is 15. However, the function automatically gives you the probability that you will hear x or fewer calls, so you either need to subtract this from 1 to get the probability that you hear x or more calls OR you can include "lower = FALSE" in your argument which will direct the function to take the upper end of the probability distribution from the specified x.

```{r}
barplot(one, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability of more than 8 calls")
```


2. What is the probability that she will hear no calls in a session?
```{r}
x <- 0 #set x equal to 0 to indicate that she heard zero calls 
l <- 15 #set l equal to the mean
two <- dpois(x = x, lambda = l, log = FALSE)
two
```

NK: You can write the function as you did or you can plug the numbers into the argument. Ex: dpois(0, 15) will also give you the same answer. It's actually not necessary to assign dpois to a variable in order for it to spit out an answer, although it works both ways.

3. What is the probability that she will hear exactly 3 calls in a session?

```{r}
x <- 3
l <- 15 
three <- dpois(x = x, lambda = l, log = FALSE)
three
```

NK: Same commentary as for 2. I got the same answer though! 

4. Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
l = 15
four <- dpois(x = x, lambda = l)
barplot(four, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability Mass Function over 0 ≤ x ≤ 30")
```

NK: We got the same here!

5. Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
data <- rpois(n = 104, lambda = 15) #rpois() function can be used to simulate data in the poisson distribution. n = the number of samples, lambda = mean of data 
data
```
NK: Same!

6. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30.

```{r}
?hist
hist(data, xlab = "Number of Calls", ylab = "Frequency of Calls", main = "Histogram of Simulated Call Data", xlim = range(0:30), ylim = NULL)
```
7. How does your histogram compare to the shape of the probability mass function you plotted above?

The probability mass function illustrates a perfect Poisson distribution and therefore does not include any random error. Conversely, my simulates data is random and therefore includes some random error which causes it to not resemble the probability mass function perfectly. However, the simulated data still centers around the mean of 15 

NK: I had a similar answer. As sample size increases, the histogram resembles the probability mass function more. 

Challenges: 
1. I struggled with figure out what "x" should be in the dpois function

